Automated Verification of Stand-alone Solar Photovoltaic Systems

### 2019-04-08 Tex/elsevier/trindade_ren_and_sust_rev1.tex
added comments
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

%------------------------------------------
\subsection{Objectives and Setup}
\label{sec:setup}
%------------------------------------------
Our experimental evaluation aims to answer two research questions:
%
\begin{enumerate}
\item[RQ1] \textbf{(soundness)} Does the automated verification provide correct results?
\item[RQ2] \textbf{(performance)} How do the verifiers compare to each other and to a simulation commercial tool?
\end{enumerate}

@@

Worth to mention that a UNKNOWN result from the verification engines means that the result is not SAT or UNSAT. This result indicates that the verification created a out of memory or a time out situation. It is possible yet, that the UNKNOWN can be caused by user interruption, however this is not an option during the tests performed during the experimentation.

>>>>

%------------------------------------------
\subsection{Objectives and Setup}
\label{sec:setup}
%------------------------------------------
Our experimental evaluation aims to answer two research questions:
%
\begin{enumerate}
\item[RQ1] \textbf{(soundness)} Does our automated verification approach provide correct results?
\item[RQ2] \textbf{(performance)} How do the verifiers compare to each other and to a simulation commercial tool?
\end{enumerate}

@@

Note that an UNKNOWN result from the verification engines means that the result is not SAT or UNSAT \textcolor{red}{What does SAT or UNSAT mean?}. This result indicates that the verification created an out of memory or a time out situation. \textcolor{red}{This sentence is totally unclear... It is possible yet that the UNKNOWN can be caused by user interruption, however this is not an option during the tests performed during the experimentation.}
